\renewcommand{\labelsep}{1.5em} 

\begin{thebibliography}{99}
\bibitem{air-quality}IQAir. "World air quality report.'' Internet: \url{https://www.iqair.com/newsroom/waqr-2023-pr}, Dec. 01, 2024

\bibitem{baocaoonhiem}V. P. Nguyen, Q. B. Ho, H. N. K. Vu, T. T. Nguyen, Q. Le, R. Rakholia, and R. S. Carbajo. "Tác động của ô nhiễm không khí đến sức khỏe người dân tại TP. Hồ Chí Minh và xây dựng giải pháp bảo vệ sức khỏe người dân,'' \textit{Tạp chí Môi trường}, vol. 01, pp. 44-50, Mar. 2022

\bibitem{LEONG2020103208}W. C Leong, R. O. Kelani, and Z. Ahmad. "Prediction of air pollution index (API) using support vector machine (SVM),'' \textit{Journal of Environmental Chemical Engineering}, vol. 08, pp. 103208, Jun. 2020

\bibitem{paper_bang}R. Rakholia, Q. Le, K. Vu, B. Q. Ho, and R. S. Carbajo. "AI-based air quality $PM_{2.5}$ forecasting models for developing countries: A case study of Ho Chi Minh City, Vietnam,'' \textit{Journal of Environmental Chemical Engineering}, vol. 46. pp. 101315, Dec. 2022

\bibitem{ann-rnn}Z. Zhao, J. Qin, Z. He, H. Li, Y. Yang, and R. Zhang. "Combining forward with recurrent neural networks for hourly air quality prediction in Northwest of China,'' \textit{Environmental Science and Pollution Research}, vol. 27, pp. 28931–28948, May. 2020

\bibitem{article-ssa}H. Hassani. "Singular Spectrum Analysis: Methodology and Comparison,'' \textit{Journal of Data Science}, vol. 5, pp. 239-257, Apr. 2007

\bibitem{pmlr-v80-yoon18a}J. Joon, J. Jordon, and M. Schaar. "GAIN: Missing Data Imputation using Generative Adversarial Nets,'' in 
\textit{Proceedings of the 35th International Conference on Machine Learning}, Stockholm, Sweden, 2018, pp. 5689--5698

\bibitem{article-vanhua}V. Hua, T. Nguyen, M. S. Dao, H. D. Nguyen, and B. T. Nguyen. "The impact of data imputation on air quality prediction problem,'' \textit{PLOS ONE}, vol. 19, Sep. 2024

\bibitem{little2019statistical}R. Litte and D. Rubin. (2019, Apr. 12). \textit{Statistical Analysis with Missing Data} ($3^{rd}$ edition). [Online]. Available: \url{https://books.google.com.vn/books?id=BemMDwAAQBAJ}

\bibitem{SONG20082361}Q. Song, M. Shepperd, X. Chen, and J. Liu. "Can k-NN imputation improve the performance of C4.5 with small software project data sets? A comparative evaluation,'' \textit{Journal of Systems and Software}, vol. 81, pp. 2361-2370, Dec. 2008

\bibitem{dbscan}M. Ester, H. P. Kriegel, J. Sander, and X. Xu. "A density-based algorithm for discovering clusters in large spatial databases with noise,'' in \textit{Proceedings of the Second International Conference on Knowledge Discovery and Data Mining}, Portland, 1996, pp. 226-231

\bibitem{dbscan-img}F. Omarzai. "DBSCAN In Depth.'' Internet: \url{https://medium.com/@fraidoonomarzai99/dbscan-in-depth-3fa4a8dbd3af}, Jul. 20, 2024

\bibitem{mice}S. V. Buuren, J. P. L. Brand, C. G. M. Groothuis-Oudshoorn, and D. B. Rubin. "Fully conditional specification in multivariate imputation,'' \textit{Journal of Statistical Computation and Simulation}, vol. 76, pp. 1049-1064, 2006

\bibitem{mlp-img}N. Lunge. "A Deep Architecture: Multi-Layer Perceptron.'' Internet: \url{https://medium.com/@nlunge786/a-deep-architecture-multi-layer-perceptron-164bc5ff3842}, Mar. 24, 2024

\bibitem{rnn-img}S. Singh. "Types of neural networks: Recurrent Neural Networks.'' Internet: \url{https://medium.com/@shekhawatsamvardhan/types-of-neural-networks-recurrent-neural-networks-7c43bd73e033}, Jan. 02, 2024

\bibitem{lstm}S. Hochreiter and J. Schmidhuber. "Long short-term memory,'' \textit{Neural computation}, vol. 9, pp. 1735-1780, 1997

\bibitem{cfnn}B. Warsito, R. Santoso, Suparti, and H. Yasin. "Cascade Forward Neural Network for Time Series Prediction,'' \textit{Journal of Physics: Conference Series}, vol. 1025, pp. 012097, May. 2018

\bibitem{esn}H. Jaeger. "The echo state approach to analysing and training recurrent neural networks-with an erratum note,'' \textit{Bonn, Germany: German National Research Center for Information Technology GMD Technical Report}, vol. 148, pp. 13, 2001

\bibitem{esn-img}G. Li, B.-J. Li, X.-G. Yu, and C.-T. Cheng. "Echo State Network with Bayesian Regularization for Forecasting Short-Term Power Production of Small Hydropower Plants,'' \textit{Energies}, vol. 8, pp. 12228-12241, Oct. 2015

\bibitem{momentum}I. Sutskever, J. Martens, G. Dahl, and G. Hinton. "On the importance of initialization and momentum in deep learning,'' in \textit{Proceedings of the 30th International Conference on Machine Learning}, Atlanta, 2013, pp. 1139-1147

\bibitem{adam}D. P. Kingma and J. Ba. "Adam: A Method for Stochastic Optimization,'' \textit{CoRR}, vol. abs/1412.6980, 2014

\bibitem{AWWA_WaterLossControl}American Water Works Association (AWWA). "Water Loss Control.'' Internet: \url{https://www.awwa.org/resource/water-loss-control/}, 2020

\bibitem{SAWACO_WaterLoss}SAWACO. "TP HCM tiêu thụ gần 2 triệu m³ nước mỗi ngày.'' Internet: \url{https://sawaco.com.vn/post-detail/tp-hcm-tieu-thu-gan-2-trieu-m%C2%B3-nuoc-moi-ngay-231026163120.html}, 2023

\bibitem{HN_WaterLoss}CÔNG TY TNHH MỘT THÀNH VIÊN NƯỚC SẠCH HÀ NỘI. "Nâng cao năng lực quản lý hệ thống cấp nước và giảm nước thất thoát tại Hà Nội.'' Internet: \url{http://hawacom.vn/?p=10936}

\bibitem{LeakDB}S. G. Vrachimis, M. S. Kyriakou, D. G. Eliades, and M. M. Polycarpou. "LeakDB Dataset.'' Zenodo, Oct. 2024. doi: 10.5281/zenodo.13985057

\bibitem{EPANET_EPA}U.S. Environmental Protection Agency. "EPANET.'' Internet: \url{https://www.epa.gov/water-research/epanet}

\bibitem{WaterGEMS_Consoft}Consoft. "WaterGEMS.'' Internet: \url{https://www.consoft.vn/hydraulics--hydrology/watergems.html}

\bibitem{MOC_NhuCauNuocSinhHoat}Bộ Xây dựng. "Nhu cầu sử dụng nước sinh hoạt tăng khoảng 5\% mỗi năm.'' Internet: \url{https://moc.gov.vn/vn/_layouts/15/NCS.Webpart.MOC/mt_poup/Intrangweb.aspx?IdNews=78334}, 2023

\bibitem{WHO_JMP_2023}World Health Organization and UNICEF. "More than 2 billion people lack access to safely managed drinking water.'' Internet: \url{https://www.who.int/news-room/fact-sheets/detail/drinking-water}, 2023

\bibitem{Hydraulic_Modeling}M. E. Girma, E. B. Zeleke, and S. L. Abebe. "Water leakage detection and localization using hydraulic modeling and classification,'' \textit{Journal of Hydroinformatics}, vol. 23, no. 4, pp. 782-794, May 2021

\bibitem{BANJARA2020104243}N. K. Banjara, S. Sasmal, and S. Voggu. "Machine learning supported acoustic emission technique for leakage detection in pipelines,'' \textit{International Journal of Pressure Vessels and Piping}, vol. 188, pp. 104243, 2020

\bibitem{Sahin2023}E. Şahin and H. Yüce. "Prediction of Water Leakage in Pipeline Networks Using Graph Convolutional Network Method,'' \textit{Applied Sciences}, vol. 13, no. 13, pp. 7427, 2023

\bibitem{Wu2024}W. Wu, X. Pan, Y. Kang, Y. Xu, and L. Han. "To Feel the Spatial: Graph Neural Network-Based Method for Leakage Risk Assessment in Water Distribution Networks,'' \textit{Water}, vol. 16, no. 14, pp. 2017, 2024

\bibitem{Sousa2023}D. P. Sousa, R. Du, J. M. B. da Silva Jr, C. C. Cavalcante, and C. Fischione. "Leakage detection in water distribution networks using machine-learning strategies,'' \textit{Water Supply}, vol. 23, no. 3, pp. 1115-1126, Feb. 2023

\bibitem{Scarselli2009}F. Scarselli, M. Gori, A. C. Tsoi, M. Hagenbuchner, and G. Monfardini. "The Graph Neural Network Model,'' \textit{IEEE Transactions on Neural Networks}, vol. 20, no. 1, pp. 61-80, 2009

\bibitem{Kipf2017}T. N. Kipf and M. Welling. "Semi-supervised classification with graph convolutional networks,'' \textit{arXiv preprint arXiv:1609.02907}, 2017

\bibitem{Velickovic2018}P. Veličković, G. Cucurull, A. Casanova, A. Romero, P. Liò, and Y. Bengio. "Graph attention networks,'' \textit{arXiv preprint arXiv:1710.10903}, 2018

\bibitem{Hamilton2017}W. L. Hamilton, R. Ying, and J. Leskovec. "Inductive representation learning on large graphs,'' \textit{arXiv preprint arXiv:1706.02216}, 2017

\bibitem{Warad2024}A. Warad, K. Wassif, and N. Ramadan. "An ensemble learning model for forecasting water-pipe leakage,'' \textit{Scientific Reports}, vol. 14, May 2024

\bibitem{Fan2021}X. Fan, X. Zhang, and B. Yu. "Machine learning model and strategy for fast and accurate detection of leaks in water supply network,'' \textit{Journal of Infrastructure Preservation and Resilience}, vol. 2, Apr. 2021

\bibitem{Tom2018}T. N. Jensen, V. Puig, J. Romera, C. S. Kallesøe, R. Wisniewski, and J. D. Bendtsen. "Leakage localization in water distribution using data-driven models and sensitivity analysis,'' \textit{IFAC-PapersOnLine}, vol. 51, no. 24, pp. 736-741, 2018

\bibitem{Mashford2012}J. Mashford, D. De Silva, S. Burn, and D. Marney. "LEAK DETECTION IN SIMULATED WATER PIPE NETWORKS USING SVM,'' \textit{Applied Artificial Intelligence}, vol. 26, no. 5, pp. 429--444, 2012

\bibitem{Zhang2023}X. Zhang, J. Shi, M. Yang, X. Huang, A. S. Usmani, G. Chen, J. Fu, J. Huang, and J. Li. "Real-time pipeline leak detection and localization using an attention-based LSTM approach," \textit{Process Safety and Environmental Protection}, vol. 174, pp. 460-472, 2023. doi: https://doi.org/10.1016/j.psep.2023.04.020

\bibitem{schafer2002missing}J. L. Schafer and J. W. Graham. "Missing data: our view of the state of the art,'' \textit{Psychological methods}, vol. 7, no. 2, pp. 147--177, 2002

\bibitem{malhotra2016lstm}P. Malhotra, L. Vig, G. Shroff, and P. Agarwal. "LSTM-based encoder-decoder for multi-sensor anomaly detection,'' in \textit{International Conference on Anomaly Detection (ADML)}, 2016

\bibitem{hundman2018detecting}K. Hundman, V. Constantinou, C. Laporte, I. Colwell, and D. Soderstrom. "Detecting spacecraft anomalies using LSTMs and nonparametric dynamic thresholding,'' in \textit{Proceedings of the 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining}, 2018, pp. 387--395

\bibitem{zhou2000pattern}S. L. Zhou, T. A. McMahon, A. Walton, and J. Lewis. "Pattern discovery and analysis of water consumption data,'' \textit{Journal of Water Resources Planning and Management}, vol. 126, no. 1, pp. 45--50, 2000

\bibitem{yang2019urban}J. Yang, Z. Shen, W. Wang, and K. Xu. "Urban water consumption prediction based on deep learning approach,'' \textit{Water}, vol. 11, no. 5, pp. 956, 2019

\bibitem{ratnam2020real}S. Ratnam and T. Banerjee. "Real-time water demand forecasting using LSTM networks,'' \textit{Procedia Computer Science}, vol. 170, pp. 654--661, 2020

\bibitem{willmott2005advantages}C. J. Willmott and K. Matsuura. "Advantages of the mean absolute error (MAE) over the root mean square error (RMSE) in assessing average model performance,'' \textit{Climate research}, vol. 30, no. 1, pp. 79--82, 2005

\bibitem{chung2020comprehensive}J. S. Chung, H. J. Lee, and E. J. Kim. "A comprehensive overview of loss functions in machine learning,'' \textit{Journal of Artificial Intelligence Research}, vol. 69, pp. 743--770, 2020

\bibitem{kingma2014adam}D. P. Kingma and J. Ba. "Adam: A Method for Stochastic Optimization,'' \textit{arXiv preprint arXiv:1412.6980}, 2014

\bibitem{ruder2016overview}S. Ruder. "An overview of gradient descent optimization algorithms,'' \textit{arXiv preprint arXiv:1609.04747}, 2016

\bibitem{goodfellow2016deep}I. Goodfellow, Y. Bengio, and A. Courville. \textit{Deep Learning}. MIT press, 2016

\end{thebibliography}

% \bibliographystyle{ieee}
% \bibliographystyle{ieeetr}
% \bibliography{component/refs}
